Arbitrary Precision and Arbitrary $n$-Grams

### 2011-03-01 paper/paper.Rnw
blarg

\subsection*{Perplexity of test set}
We evaluated our model on the test set by computing
the perplexity of the test set. In addition to the variables
above, we ran this test with smoothing on and with smoothing off.
We hypothesized that smoothing would reduce perplexity.

@@

For each combination of the intependent variables, we
generated 23 sentences from the \emph{War and Peace} corpus
and tested their perplexity. %ADD SHAKESPEARE

@@

\subsection*{Pelplexity of test set}

\subsection*{Perplexity of generated sentences}
Perplexity of generated sentences decreased with increased
\ngram length

>>>>

\subsection*{Perplexity of test set}
We evaluated our model on the test set by computing
the perplexity of the test set. In addition to the variables
above, we ran this test with smoothing on and with smoothing off.

@@

For each combination of the intependent variables, we
generated 23 sentences from the \emph{War and Peace} corpus
and tested their perplexity. We did the same the Shakespeare corpus
but generated only 7 sentences for each treatment combination.

@@

\subsection*{Pelplexity of test set}
For each corpus, perplexity of test set decreased when the models
were run for longer $n$-grams, and the perplexity
leveled off starting at $n=3$ (figure \ref{fig:test}). Probability computation type had no effect.

Smoothing slightly increased perplexity. The increase
was larger for larger $n$.

\begin{figure}
\begin{center}
<<echo=F,fig=T,height=9>>=
test.plot()
@
\end{center}
\caption{\label{fig:test}Perplexities of the test corpora by $n$-gram length and probability computation method for models trained on the respective training corpora.}
\end{figure}

\subsection*{Perplexity of generated sentences}
Perplexity of generated sentences decreased with when longer $n$-grams
were used in the model (figure \ref{fig:gen}). The perplexity
leveled off starting at $n=3$. Probability computation type did not
affect perplexity.
